Regression Cube Analysis of Cohort Study Data

### 2015-03-26 draft.tex
minor changes on Evaluation
added first part of Application section with Ulis analysis

In \cite{Niemann2014}, the authors show that women and men exhibit differences in the class distribution of the liver fat concentration.
%%
Also, for women they identify that there is a association between age and liver fat concentration.
%%
They compute an appropriate cut-off value of 52 years for which the class distribution is most homogeneous within the resulting subsets.
%%
Based on this observations, we perform our analysis on three sub-populations, $PartitionF$, $PartitionM$ and \emph{$F:age\>52$}.
%%
\subsection{Case 1: Hypothesis-free Analysis of the Breast Cancer Data Set}
%%
The analysis goal is to find relationships on the breast cancer data using features derived from the mammography analysis.
%%
Relationships between the share of parenchyma tissue on the overall breast volume are of high interest \cite{Mccormack2006}.
%%

\subsection{Case 2: Hypothesis-driven Analysis of the Hepatic Steatosis Data Set}
%%
\com{1. Can we reconstruct relationships based on the regression cube?}

\com{2. How does the numeric target feature influence the result?}
\subsection{Further Feedback and Lessons Learned} \label{Lessons Learned}
%%
\textbf{Extracted Hypotheses have to investigated further.}
\com{Tills Feedback - Regression analysis also incorporates assumptions about the data, }
%%

@@

>>>>

In \cite{Niemann2014}, the authors show that women and men exhibit differences in the class distribution of the liver fat concentration.
%%
Also, for women they identify that there is a association between age and liver fat concentration.
%%
They compute an appropriate cut-off value of 52 years for which the class distribution is most homogeneous within the resulting subsets.
%%
Based on this observations, we perform our analysis on three sub-populations, \emph{females}, \emph{males} and \emph{females} older than 52 years.
%%
\subsection{Case 1: Hypothesis-free Analysis of the Breast Cancer Data Set}
%%
The analysis goal is to find relationships on the breast cancer data using features derived from the mammography analysis.
%%
Relationships between the share of parenchyma tissue on the overall breast volume are of high interest \cite{Mccormack2006}.
%%

\subsection{Case 2: Hypothesis-driven Analysis of the Hepatic Steatosis Data Set}
%%
The goal at the beginning of the analysis was to reproduce results based on the prior analysis.
%%
Subjects with a fatty liver could be identified using somatometric features, hepatic steatosis indicator-features as well as creatinine (\com{important for kidney}) and uric acid (\com{gout, diabetes}) magnitudes.
%%
The analysis was started with the target feature \emph{liver fat content} (\emph{mrt\_liverfat\_s2}), which was derived from the MRI data analysis.
%%
UN therefore started the calculation using the formula $mrt\_liverfat\_s2 \sim X + Y + Z$.
%%
The data set containing all \emph{males} showed broad consensus with the expected results.
%%
The 3D-cube showed highlighted features at the end of the cube (Fig.~\ref{fig:application} a).
%%
Using the mouse-slicing allowed for fast navigation to the respective features.
%%
They include indicators hepatic steatosis ($R^2$:XX) as well as somatometric features, such as \emph{body mass index} (\emph{BMI}) and waist circumference.
%%
Feature correlations with \emph{gamma-glutamyl transpeptidase} (\emph{GGT}, indicating damaged livers if elevated) were found, but with low $R^2$ of XX.

%%
UN analyzed both \emph{female} groups in the same manner, concluding with the same findings regarding \emph{somatometric} features as well as \emph{hepatic steatosis} indicators.
%%
Using the mosaic plot, relationships incorporating enzyme used for the diagnosis of liver dysfunctions were found, e.g. aspartate aminotransferase.
%%

For most features, UN found at least tendencies using our approach.
%%
Due to the difference between our regression-model approach and the decision-tree approach presented in \cite{Niemann2014}, a complete matching set of correlating features are not expected.

%Regression cube calculations were carried out for

\textbf{Analysis of non-discretized target feature.}
The target feature derived from the MRI image data was discretized in \cite{Niemann2014} as decision trees algorithms require a categorical target feature.
%%
Since the \emph{regression cubes} analysis is not restricted in this way, UN applied the same analysis for \emph{males} and the two female group using its whole data range.
%%

Using the \emph{Regression Cube}, UN 
\textbf{Interleukin-6 correlation with liver fat.}

\com{ToDo: Reflect on the different methods - one is used to define subsets which define the target feature very well, the other looks how good the features describe the target itself}
\com{1. Can we reconstruct relationships based on the regression cube?}

\com{2. Does discretization of the numeric target feature influence the result?}

\subsection{Further Feedback and Lessons Learned} \label{Lessons Learned}
%%
\textbf{Extracted Hypotheses have to investigated further.}
\com{Tills Feedback - Regression analysis also incorporates assumptions about the data, }
%%

@@

\textbf{Attention steering is crucial.}
\com{Bring important events to the users attention, otherwise it might be overlooked!}
